Word-Level Abstractions for Sequential Design Verification using Algebraic Geometry

### 2016-12-14 dissertation/slides/defense.tex
dissertation defense slides v1: milestone

% \usepackage{helvet}
% \usepackage{enumerate}
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{graphicx}
% \usepackage{ulem}
\usepackage{multirow}
\usepackage{comment}
\usepackage{xspace}
%\usepackage{columns}

@@

	\item Projection

@@

\item Word-level reachability analysis -- analog if implicit state enumeration

@@

	\item {\bf A:} Datapath $\gets$ word-level info 

@@

\item Apply word-level reachability algo. to sequential arithmetic circuit verification

@@

@@

	\item Apply UNSAT core to $k$-BMC abstraction refinement

@@

@@

@@

\item Word-level techniques (term rewriting, uninterpreted function): ?

@@

@@

\begin{Theorem}[Fermat's Little Theorem over $\Fq$]
Let $\alpha \in \Fq$, then $\alpha^q = \alpha$. Therefore, $x^q -x$
vanishes on all points in $\Fq$. 
\end{Theorem}
\begin{table}[H]
\label{tab:truthtable}
\centering{\small
\begin{tabular}{|c|ccc|c|}
\hline
$\{a_2a_1a_0\}\in\mathbb{B}^3$   & $A\in \F_{2^3}$ &$\rightarrow$& $\{z_2z_1z_0\}\in\mathbb{B}^3$  & $Z\in \F_{2^3}$ \\
\hline
000  &0 &$\rightarrow$&000 & 0 \\
001  &1 &$\rightarrow$&001 & 1 \\
010  &$\alpha$ & $\rightarrow$ & 111& $\alpha^2 + \alpha + 1$ \\
011  &$\alpha + 1$ &$\rightarrow$& 111 & $\alpha^2 + \alpha + 1$ \\
100  &$\alpha^2$ &$\rightarrow$& 101 &  $\alpha^2+1$ \\
101  &$\alpha^2 + 1$ &$\rightarrow$&011 & $\alpha+1$ \\
110  &$\alpha^2 + \alpha$&$\rightarrow$& 101 &$\alpha^2 + 1$ \\
111  &$\alpha^2 + \alpha + 1$ &$\rightarrow$& 101 &$\alpha^2 + 1$\\
\hline
\end {tabular}
}
\caption{Truth table for mappings in $\mathbb{B}^3$ and $\F_{2^3}$}
\end{table}
\pause
\bi
\item A polynomial function representation always exists in $\Fq[A]$ (Lagrange's interpolation)
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Computer algebra terminology}}
\vspace{-0.2in}
%\ptsize{10}
Let $\mathbb{F}_q = GF(2^k)$, and $\overline{\Fq}$ be its closure
\begin{itemize}
\item $\mathbb{F}_q[x_1, \ldots, x_n]$: ring of all polynomials with
  coefficients in $\mathbb{F}_q$

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Polynomial division}}
Copy page 12 from FMCAD
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Algebraic geometry terminology (cont.)}}
Let $\mathbb{F}_q = GF(2^k)$:
\begin{itemize}
\item $\mathbb{F}_q[x_1, \ldots, x_n]$: ring of all polynomials with
  coefficients in $\mathbb{F}_q$ 
\item Given a set of polynomials:
\begin{itemize}
\item $f, f_1, f_2, \dots , f_s \in \mathbb{F}_q[x_1, \dots, x_n]$
\item Find solutions to $f_1 = f_2 = \dots = f_s = 0$
\end{itemize}
\item \alert{Variety:} Set of ALL solutions to a given system of polynomial equations: $V(f_1, \dots, f_s)$
	\begin{itemize}
	\item In $\mathbb{R}\left[x,y\right]$, $V(x^2+y^2-1)=\{all\  points\  on\ circle: x^2+y^2-1=0\}$
	\item In $\mathbb{R}[x]$, $V(x^2+1)=\emptyset$
	\item In $\mathbb{C}[x]$, $V(x^2+1)=\{(\pm i)\}$
	\end{itemize}
\item Variety depends on the \alert{ideal} generated by the polynomials.
\item Reason about the Variety by analyzing the Ideals
\end{itemize}
\end{frame}

@@

\begin{Definition}
{\bf Ideals of Polynomials:} Let $f_1, f_2, \ldots, f_s \in
\mathbb{F}_q[x_1, \dots, x_n]$. Let 
\begin{eqnarray}
J = \langle f_1, f_2 \ldots, f_s\rangle = \{f_1 h_1 + f_2 h_2 + \dots + f_s h_s\} \nonumber 
\end{eqnarray}

@@

\begin{frame}{\large{Preliminaries: Buchberger's algorithm}}

@@

\item Inspiration of mapping: set of states $\to$ \alert{variety} of polynomial ideal

@@

\item GB($I_{x,y,z}$)$\cap\Fq[z]\Leftrightarrow$ \alert{projection} on variable $z$!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Complement set in algebraic geometry}}
\begin{Definition}
({\bf Quotient of Ideals}) If $I$ and $J$ are ideals in $\mathbb
  F[x_1, \dots, x_n]$, then $I:J$ is the set
  \begin{equation}
  \{f \in \mathbb F[x_1, \dots, x_n]\ |\ f\cdot g \in I, \forall g \in J\}\nonumber
  \end{equation}
and is called the {\bf ideal quotient} of $I$ by $J$.
\end{Definition}
\begin{Theorem}
\label{thm:quotient}
Let $J_0$ be an ideal of vanishing polynomials over $\Fkk[x_1,\dots,x_n]$, then 
$${\bf V}(J_0:J) = {\bf V}(J_0) - {\bf V}(J) = \overline{{\bf V}(J)}$$
\end{Theorem}
\bi
\item Given ideal $J$, compute $J'$ s.t. $V(J') = \overline{V(J)}$
\item $\to J'=J_0:J$
\ei
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Full Blown traversal of example circuit using algebraic geometry}}
\bi
\item Initial state $from^0 = S(\{00\})$
\item {\bf Iteration 1:}Compose an elimination ideal $J$ 
\vspace{-0.2in}\\
\begin{align*}
&f_1: t_0- (xs_0s_1+xs_0+xs_1+x+s_0+s_1+1)\\
&f_2: t_1 - (xs_0+x+s_0s_1+s_0)\\
&f_3: S - s_0 - s_1\alpha\\
&f_4: T - t_0 - t_1\alpha
\end{align*}
$J_{ckt} = \langle f_1,f_2,f_3,f_4\rangle$
\begin{align*}
&f_5: x^2-x\\
&f_6: s_0^2-s_0, f_7: s_1^2-s_1\\
&f_8: t_0^2-t_0, f_9: t_1^2-t_1\\
&f_{10}: S^4-S, f_{11}:T^4-T
\end{align*}
$\ \ \ \ \ \ \ \ \ \ \  \ J_0 = \langle f_5,f_6,\dots,f_{11}\rangle$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = pptpage2]{\large{Full Blown traversal of example circuit using algebraic geometry}}
\bi
\item Elimination term order: 
$$\{x,s_0,s_1,t_0,t_1\}~(all~bits)~>~S~(PS~word)~ >~ T~(NS~word)$$
\item Compute the reduced GB for $J = J_{ckt}+J_0+\langle from^0\rangle$
\item Next state 
$$to^1 = \langle T^2+(\alpha+1)T+\alpha\rangle$$ 
\item Mapping to set of states
$$V(to^1) = \{1,\alpha\} \Leftrightarrow \{01,10\}$$
\item Complement of formerly reached state:
$$\langle T^4-T\rangle:\langle T\rangle = \langle T^3+1\rangle$$ 
\item Mapping to set of states
$$V(\langle T^3+1\rangle) = \{1,\alpha,1+\alpha\} \Leftrightarrow \{01,10,11\}$$
\ei
\hyperlink{linkSTG}{\beamergotobutton{STG}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = pptpage3]{\large{Full Blown traversal of example circuit using algebraic geometry}}
\bi
\item Newly reached states:
$$\langle T^3+1, T^2+(\alpha+1)T+\alpha \rangle = \langle T^2+(\alpha+1)T+\alpha \rangle~(\{01,10\})$$ 
\item Update current reached states 
$$reach = \langle T\cdot T^2+(\alpha+1)T+\alpha \rangle = \langle T^3+(\alpha+1)T^2+\alpha T\rangle$$ 
\item Mapping to set of states
$$V(reached) = \{0,1,\alpha\} \Leftrightarrow \{00,01,10\}$$
\item Update the present states for next iteration
$$from^1 = \langle S^2+(\alpha+1)S+\alpha\rangle$$
\ei
\hyperlink{linkSTG}{\beamergotobutton{STG}}
\end{frame}

@@

\begin{frame}{\large{Improve complexity using RATO}}

@@

\item Benefit: Only one pair of poly with non-relatively-prime leading terms\par
$gcd(lt(f_w),lt(f_g))\neq 1$

@@

@@

\item $Spoly$ reduction gives $T+\Func(inputs)$

@@

\includegraphics[width=5.5in]{./new_multi.eps}
\caption{A 3-bit RH-SMPO and its Moore FSM model}

@@

\begin{frame}{\large{GF multiplier verification algo.}}

@@

  $from_0(R,A,B) = \langle R, \mathcal{G}(A_{init}), \mathcal{H}(B_{init})\rangle$\;
  $i = 0$\;
  \Repeat{$i == k$}
  {
  	$i \gets i + 1$\;
	\alert{$f_o \xrightarrow{J + J_0+ from_{i-1}(R,A,B)}_+ f_r$ under RATO} \;
	\alert{$to_i(R',A',B')\gets f_r(\{R',A',B'\}\setminus\{r_0,\dots,r_{k-1},a_0,\dots,a_{k-1},b_0,\dots,b_{k-1}\}$}\;
	$from_i \gets to_i(\{R,A,B\}\setminus \{R',A',B'\})$\;
  }
\Return{$from_k(R_{final})$}
\caption {Abstraction via implicit unrolling for Sequential GF circuit verification}
\end{algorithm}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Experiment result: sequential GF multiplier verification}}
\begin{table}[H]
\centering
\caption{\small Run-time for verification of bug-free RH-SMPO circuits
  for SAT, ABC and BDD based methods. \emph{TO} = timeout 14 hrs}
\label{tbl:equiv}
\begin{tabular}{|c||c|c|c|c|} 
\hline
& \multicolumn{4}{|c|}{Word size of the operands $k$-bits}  \\
\hline
Solver & 11 & 18 & 23 & 33 \\
\hline
\hline
Lingeling & 593  & \emph{TO}  & \emph{TO}  & \emph{TO}\\
\hline
\hline
ABC & 6.24 & \emph{TO} & \emph{TO} & \emph{TO}\\
\hline
\hline
BDD & 0.1 & 11.7 & 1002.4 & \emph{TO}  \\
\hline
\end{tabular}
\label{table:satbdd}  
\end{table} 
\begin{table}[H]
\centering
\label{tab:Cpp}
{\small 
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c||}{\centering Operand size $k$} & 36 & 60 & 81 & 100 & 131 & 162 \\
\hline
\multirow{2}{1.5cm}{\centering RH-SMPO} & \#Polynomials & 4716 & 12960 & 21870 & 35600 & 56592 & 92826 \\
\cline{2-8}
 & Runtime & 14.3 & 213.3 & 1343 & 4685 & 26314 & 124194 \\
\hline
\multirow{2}{1.5cm}{\centering Agnew's SMPO} & \#Polynomials & 2700 & 7380 & 13356 & 20300 & 34715 & 52974 \\
\cline{2-8}
 & Runtime & 10.2 & 212.0 & 2684 & 4686 & 56568 & 119441 \\

@@

\end{tabular}
}
\end{table}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Refutation within Buchberger's algo.}}
\bi
\item Recall Buchberger's algo....
\pause
\item  What can we learn from the \alert{``1" generated by Buchberger's Algorithm}?
\ei
\begin{Theorem}
\label{thm:weak-ns}
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_d]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_d] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$

>>>>

% \usepackage{helvet}
% \usepackage{enumerate}
% \usepackage{amsmath}
% \usepackage{amsfonts}
% \usepackage{graphicx}
% \usepackage{ulem}
\usepackage{multirow}
\usepackage{comment}
\usepackage{xspace}
\usepackage{polynom}
%\usepackage{columns}

@@

	\item Projection of varieties

@@

\item Word-level reachability analysis -- analog of implicit state enumeration

@@

	\item {\bf A:} Data $\gets$ word-level info 

@@

\item Apply word-level reachability algorithm to sequential arithmetic circuit verification

@@

            \item Word-level abstraction from bit-level ckts [Pruss, 2015]

@@

@@

	\item Usually based on reachability analysis

@@

	\item Induction-based

@@

\item Word-level techniques (term rewriting, uninterpreted function): ?/no encoding

@@

\begin{frame}{\large{Working field: $\Fkk$}}
\item Our proposed state-space model is based on finite field $\Fkk$
	\item $\B^k$: bit-vector
	\item $\Z_{2^k}$, $\R_q$: approaches not compatible
\item Evaluations in $\B^k \Leftrightarrow$ Elements in $\Fkk$
\item Functions $\B^k\to\B^k \Leftrightarrow \Func:\Fkk\to\Fkk$

@@

\begin{Theorem}[Fermat's Little Theorem over $\Fq$]
Let $\alpha \in \Fq$, then $\alpha^q = \alpha$. Therefore, $x^q -x$
vanishes on all points in $\Fq$. 
\end{Theorem}
\begin{table}[H]
\label{tab:truthtable}
\centering{\small
\begin{tabular}{|c|ccc|c|}
\hline
$\{a_2a_1a_0\}\in\mathbb{B}^3$   & $A\in \F_{2^3}$ &$\rightarrow$& $\{z_2z_1z_0\}\in\mathbb{B}^3$  & $Z\in \F_{2^3}$ \\
\hline
000  &0 &$\rightarrow$&000 & 0 \\
001  &1 &$\rightarrow$&001 & 1 \\
010  &$\alpha$ & $\rightarrow$ & 111& $\alpha^2 + \alpha + 1$ \\
011  &$\alpha + 1$ &$\rightarrow$& 111 & $\alpha^2 + \alpha + 1$ \\
100  &$\alpha^2$ &$\rightarrow$& 101 &  $\alpha^2+1$ \\
101  &$\alpha^2 + 1$ &$\rightarrow$&011 & $\alpha+1$ \\
110  &$\alpha^2 + \alpha$&$\rightarrow$& 101 &$\alpha^2 + 1$ \\
111  &$\alpha^2 + \alpha + 1$ &$\rightarrow$& 101 &$\alpha^2 + 1$\\
\hline
\end {tabular}
}
\caption{Truth table for mappings in $\mathbb{B}^3$ and $\F_{2^3}$}
\end{table}
\pause
\vspace{-0.2in}
% \bi
% \item Always possible to generate word-level poly function using Lagrange's interpolation
% \ei
\begin{align*}
Z =& \Func(A) \\
=& (\alpha^2+\alpha+1) A^7 + (\alpha^2+1) A^6 + \alpha A^5 + (\alpha+1) A^4 \\
&+ (\alpha^2+\alpha+1)A^3+ (\alpha^2+1)A
\end{align*}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Computer algebra terminology}}
\vspace{-0.2in}
%\ptsize{10}
Let $\mathbb{F}_q = GF(2^k)$, and $\overline{\Fq}$ be its closure
\begin{itemize}
\item $\mathbb{F}_q[x_1, \ldots, x_n]$: ring of all polynomials with
  coefficients in $\mathbb{F}_q$

@@

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Polynomial division}}
Divide $f = x^3-2x^2+2x+8$ ~~by ~~$g =2x^2+3x + 1$\\

\polylongdiv{x^3-2x^2+2x+8}{2x^2+3x + 1}

\bi
\item The key step in division: \alert{$r = f - \frac{lt(f)}{lt(g)}\cdot  g$}, denoted $f\xrightarrow{g} r$
\item Similarly divide $f$ by a set of polynomials $F = \{f_1,\dots, f_s\}$
\item Denoted: $f \xrightarrow{f_1, \dots, f_s}_+ r$
\bi
\item Remainder $r$ is reduced: no term in $r$ is divisible by $lt(f_i)$
\ei
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Algebraic geometry terminology (cont.)}}
Let $\mathbb{F}_q = GF(2^k)$:
\begin{itemize}
% \item $\mathbb{F}_q[x_1, \ldots, x_n]$: ring of all polynomials with
%   coefficients in $\mathbb{F}_q$ 
\item Given a set of polynomials:
\begin{itemize}
\item $f_1, f_2, \dots , f_s \in \mathbb{F}_q[x_1, \dots, x_n]$
\item Find solutions to $f_1 = f_2 = \dots = f_s = 0$
\end{itemize}
\item \alert{Variety:} Set of ALL solutions to a given system of polynomial equations: $V(f_1, \dots, f_s)$
	\begin{itemize}
	\item In $\mathbb{R}\left[x,y\right]$, $V(x^2+y^2-1)=\{all\  points\  on\ circle: x^2+y^2-1=0\}$
	\item In $\mathbb{R}[x]$, $V(x^2+1)=\emptyset$
	\item In $\mathbb{C}[x]$, $V(x^2+1)=\{(\pm i)\}$
	\end{itemize}
\item Variety depends on the \alert{ideal} generated by the polynomials.
\item Reason about the Variety by analyzing the Ideals
\end{itemize}
\end{frame}

@@

\begin{Definition}
{\bf Ideals of Polynomials:} Let $f_1, f_2, \ldots, f_s \in
\mathbb{F}_q[x_1, \dots, x_n]$. Let 
\begin{eqnarray}
J = \langle f_1, f_2 \ldots, f_s\rangle = \{f_1 h_1 + f_2 h_2 + \dots + f_s h_s\},~~h_i\in\Fq[x_1,\dots,x_n] \nonumber 
\end{eqnarray}

@@

\begin{frame}{\large{Preliminaries: Buchberger's algorithm computes a Gr\"obner basis}}

@@

\item GB enables mapping: set of states $\to$ \alert{variety} of polynomial ideal
	\item Algebraic/reasoning engine: application to elimination
\item GB enables abstraction

@@

\item GB($I_{x,y,z}$)$\cap\Fq[z]$ related to \alert{projection} on variable $z$!

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Complement set in algebraic geometry}}
\begin{Definition}
({\bf Quotient of Ideals}) If $I$ and $J$ are ideals in $\mathbb
  F[x_1, \dots, x_n]$, then $I:J$ is the set
  \begin{equation}
  \{f \in \mathbb F[x_1, \dots, x_n]\ |\ f\cdot g \in I, \forall g \in J\}\nonumber
  \end{equation}
and is called the {\bf ideal quotient} of $I$ by $J$.
\end{Definition}
\begin{Theorem}
\label{thm:quotient}
Let $J_0$ be an ideal of vanishing polynomials over $\Fkk[x_1,\dots,x_n]$, then 
$${\bf V}(J_0:J) = {\bf V}(J_0) - {\bf V}(J) = \overline{{\bf V}(J)}$$
\end{Theorem}
\bi
\item $V(J)\subseteq \Fkk$ in affine space
\item Given ideal $J$, compute $J'$ s.t. $V(J') = \overline{V(J)} = \Fkk-V(J)\implies J'=J_0:J$
\ei
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Full Blown traversal of example circuit using algebraic geometry}}
\bi
\item Initial state $from^0 = S(\{00\})$
\item {\bf Iteration 1:}Compose an elimination ideal $J$ 
\ei
\vspace{-0.2in}
\begin{columns}[onlytextwidth]
\begin{column}{0.5\textwidth}
\begin{align*}
&f_1: t_0- (xs_0s_1+xs_0\\
&+xs_1+x+s_0+s_1+1)\\
&f_2: t_1 - (xs_0+x+s_0s_1+s_0)\\
&f_3: S - s_0 - s_1\alpha\\
&f_4: T - t_0 - t_1\alpha
\end{align*}
\end{column}
\vspace{-0.2in}
\begin{column}{0.5\textwidth}
\begin{align*}
&f_5: x^2-x\\
&f_6: s_0^2-s_0, f_7: s_1^2-s_1\\
&f_8: t_0^2-t_0, f_9: t_1^2-t_1\\
&f_{10}: S^4-S, f_{11}:T^4-T
\end{align*}
\end{column}
\end{columns}
\begin{columns}[onlytextwidth]
\begin{column}{0.7\textwidth}
\begin{figure}[H]
\centering{
\includegraphics[width=3in]{hehe.pdf}
}
\end{figure}
\end{column}
\begin{column}{0.3\textwidth}
$J_{ckt} = \langle f_1,f_2,f_3,f_4\rangle$\\
$J_0 = \langle f_5,f_6,\dots,f_{11}\rangle$
\end{column}
\end{columns}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = pptpage2]{\large{Full Blown traversal of example circuit using algebraic geometry}}
\bi
\item Elimination term order: 
$$\{x,s_0,s_1,t_0,t_1\}~(all~bits)~>~S~(PS~word)~ >~ T~(NS~word)$$
\item Compute the reduced GB for $J = J_{ckt}+J_0+\langle from^0\rangle$
\item Next state 
$$to^1 = \langle T^2+(\alpha+1)T+\alpha\rangle$$ 
\item Mapping to set of states
$$V(to^1) = \{1,\alpha\} \Leftrightarrow \{01,10\}$$
\item Complement of formerly reached state:
$$\langle T^4-T\rangle:\langle T\rangle = \langle T^3+1\rangle$$ 
\item Mapping to set of states
$$V(\langle T^3+1\rangle) = \{1,\alpha,1+\alpha\} \Leftrightarrow \{01,10,11\}$$
\ei
\hyperlink{linkSTG}{\beamergotobutton{STG}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = pptpage3]{\large{Full Blown traversal of example circuit using algebraic geometry}}
\bi
\item Newly reached states:
$$\langle T^3+1, T^2+(\alpha+1)T+\alpha \rangle = \langle T^2+(\alpha+1)T+\alpha \rangle~(\{01,10\})$$ 
\item Update current reached states 
$$reach = \langle T\cdot T^2+(\alpha+1)T+\alpha \rangle = \langle T^3+(\alpha+1)T^2+\alpha T\rangle$$ 
\item Mapping to set of states
$$V(reached) = \{0,1,\alpha\} \Leftrightarrow \{00,01,10\}$$
\item Update the present states for next iteration
$$from^1 = \langle S^2+(\alpha+1)S+\alpha\rangle$$
\ei
\hyperlink{linkSTG}{\beamergotobutton{STG}}
\end{frame}

@@

\begin{frame}{\large{Improve complexity using RATO [Pruss, '15]}}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Benefits of using RATO}}
\item Definition of RATO:\par 
``bit-level variables ordered reverse topologically "$ > T>S$
\item Only one pair of poly with non-relatively-prime leading terms
	\item If $gcd(lt(f_w),lt(f_g)) = 1$:
	\item $Spoly(f_w,f_g) \xrightarrow{J_{ckt}+J_0}_+ 0$
\item Topology in structure
	\item Each poly with leading term -- fanout
	\item Divide with levelization
	\item Only inputs (primary \& pseudo) left!

@@

\item $Spoly$ reduction gives $T+\Func(primary/pseudo~inputs)$

@@

\includegraphics[width=5in]{./new_multi.eps}

@@

\begin{frame}{\large{GF multiplier verification algorithm}}

@@

  $from_0(R,A,B) = \langle R, \mathcal{G}(A_{init}), \mathcal{H}(B_{init})\rangle$\;
  $i = 0$\;
  \Repeat{$i == k$}
  {
  	$i \gets i + 1$\;
	\alert{$f_o \xrightarrow{J + J_0+ from_{i-1}(R,A,B)}_+ f_r$ under RATO} \;
	\alert{$to_i(R',A',B')\gets f_r(\{R',A',B'\}\setminus\{r_0,\dots,r_{k-1},a_0,\dots,a_{k-1},b_0,\dots,b_{k-1}\}$}\;
	$from_i \gets to_i(\{R,A,B\}\setminus \{R',A',B'\})$\;
  }
\Return{$from_k(R_{final})$}
\caption {Abstraction via implicit unrolling for Sequential GF circuit verification}
\end{algorithm}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Experiment result: sequential GF multiplier verification}}
\bi
\item Run-time for verification of bug-free RH-SMPO circuits
  for SAT, ABC and BDD based methods. \emph{TO} = timeout 14 hrs
\begin{table}[H]
\centering
\label{tbl:equiv}
\begin{tabular}{|c||c|c|c|c|} 
\hline
& \multicolumn{4}{|c|}{Word size of the operands $k$-bits}  \\
\hline
Solver & 11 & 18 & 23 & 33 \\
\hline
\hline
Lingeling & 593  & \emph{TO}  & \emph{TO}  & \emph{TO}\\
\hline
\hline
ABC & 6.24 & \emph{TO} & \emph{TO} & \emph{TO}\\
\hline
\hline
BDD & 0.1 & 11.7 & 1002.4 & \emph{TO}  \\
\hline
\end{tabular}
\label{table:satbdd}  
\end{table} 
\item Runtime for verification of bug-free Agnew's and RH-SMPO circuits using our approach
\hspace{-0.3in}\begin{table}[H]
\centering
\label{tab:Cpp}
{\small 
\begin{tabular}{|c|c||c|c|c|c|c|c|}
\hline
\multicolumn{2}{|c||}{\centering Operand size $k$} & 36 & 60 & 81 & 100 & 131 & 162 \\
\hline
\multirow{2}{1cm}{\centering RH-SMPO} & \#Polys & 4716 & 12960 & 21870 & 35600 & 56592 & 92826 \\
\cline{2-8}
 & Runtime & 14.3 & 213.3 & 1343 & 4685 & 26314 & 124194 \\
\hline
\multirow{2}{1cm}{\centering Agnew's SMPO} & \#Polys & 2700 & 7380 & 13356 & 20300 & 34715 & 52974 \\
\cline{2-8}
 & Runtime & 10.2 & 212.0 & 2684 & 4686 & 56568 & 119441 \\

@@

\end{tabular}
}
\end{table}
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\vspace{-0.2in}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Refutation within Buchberger's algo.}}
\bi
\item Recall Buchberger's algorithm
\pause
\item  What can we learn from the \alert{``1" generated by Buchberger's Algorithm}?
\ei
\begin{Theorem}
\label{thm:weak-ns}
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_d]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_d] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$
